EuPPollNet: A European database of plant-pollinator networks

### 2024-05-14 Manuscript/EuPPollNet_Ms.qmd
paragraph 2 ongoing...

EuPPollNet offers the largest set of plant-pollinator networks and plant-pollinator studies compiled to date at European level. The database contains `r prettyNum(plant_spp_number, big.mark=",")` plant and `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator species with over a million of interaction records. While the overall sampling coverage of species and interactions is relatively high across the sampled sites, the taxonomic coverage of plants and the main pollinator groups at the European level is still relatively low (e.g., `r round(plant_coverage, 1)`% for flowering plants and `r round(bee_coverage, 1)`% for bee species). Given that most of the plant-pollinator networks from the database are sampled on pastures, and habitat heterogeneity is a crucial factor in understanding pollinator diversity at European level [@kleijn2015; @hass2018; @martinez2022], adding studies on other habitat types is likely to result in a rapid increase of the coverage of plant and pollinator species and their interactions. Plant and pollinator species are rarely shared across multiple sites, indicating that there are few "common" species and many "rare" ones at the metaweb or continental level. This high number of "rare" species results in an upward slope of the species or interaction accumulation curves [@thompson2003]. In other words, minimal sampling efforts are capturing a substantial number of species and interactions, but achieving a comprehensive inventory will require of numerous sampling events within and across habitats, particularly for plant-pollinator interactions.

Taxonomy paragraph?

>>>>

EuPPollNet offers the largest set of plant-pollinator networks and plant-pollinator studies compiled to date at European level. The database contains `r prettyNum(plant_spp_number, big.mark=",")` plant and `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator species with over a million of interaction records. While the overall sampling coverage of species and interactions is relatively high across the sampled sites, the taxonomic coverage of plants and the main pollinator groups at the European level is still relatively low (e.g., `r round(plant_coverage, 1)`% for flowering plants and `r round(bee_coverage, 1)`% for bee species). Given that most of the plant-pollinator networks from the database are sampled on pastures, and habitat heterogeneity is a crucial factor in understanding pollinator diversity at European level [@kleijn2015; @hass2018; @martinez2022], adding studies on other habitat types is likely to result in a rapid increase of the coverage of plant and pollinator species and their interactions. Plant and pollinator species were rarely shared across multiple sites, indicating that there are few "common" species and many "rare" ones at the metaweb or continental level. This high number of "rare" species results in an upward slope of the species or interaction accumulation curves [@thompson2003]. In other words, minimal sampling efforts are capturing a substantial number of species and interactions, but achieving a comprehensive inventory will require of numerous sampling events within and across habitats, particularly for plant-pollinator interactions.

Bees conducted the majority of the interactions at the metaweb level, but their relative relevance changed across habitats and bioclimatic regions. For instance, plant-pollinator communities in the Mediterranean were dominated by bees, while communities in Alpine or Boreal regions were especially fly species rich or fly-dominated. These patterns are consistent with our current understanding of bee diversity, which peaks in dry or temperate areas [@orr2021; @leclercq2023]; and with the fact that colder environments (i.e., altitude and latitude wise) harbor a larger fraction of fly pollinators compared to other taxa [@elberling1999; @lefebvre2018]. In addition, beetles were only species rich in the Mediterranean region.

Comment on
Coleoptera -sampling methodology-
Lepidoptera -Ollerton ref, global context-

Bee diversity peaked in the Mediterranean area as found in previous large scale comparisons [REF] and beetles were particularly relevant in this region

, while non-bee insects such as syrphids were particularly relevant in colder 
non-bee insect pollinators were particularly relevant

Hymenoptera and Diptera had a similar number of species, the majority of interactions were conducted by bees.

Bees conducted the majority of interactions within the database which is in agreement with previous large scale studies conducted in Europe [REF].

and for the majority of Angiosperm species worldwide [@ollerton2017]. The proportion of the major pollinator orders within the database

Despite Hymenoptera and Diptera species have a similar number of species within the database, bees conducted most of the interactions as found in previous large scale studies [@Lanuza2023].

Ollerton
Myself
Someone else?
